### 2015-05-19 inst/examples/ipm_sims_example.Rmd
adds figure for looking a relation to niche difference

>>>>

## Comparison with niche differecnes
```{r niches}
niche_diff <- data.frame(site=sites,
                         ND = c(0.58, 0.59, 0.66, 0.69, 0.68))
pgr_subs <- subset(pgr_synch, L2!="ENVDEMO")
pgr_cast <- dcast(pgr_subs, L1~L2, value.var = "value")
synch_diff <- ddply(pgr_cast, .(L1), summarise,
                    value = ENV-DEMO)
niche_synch <- merge(niche_diff, synch_diff, by.x="site", by.y="L1")
ggplot(niche_synch, aes(x=ND, y=value))+
  geom_point(size=5)
```
